Highlights

### 2018-12-06 Papers/AppliedMaths2018/Resubmission/Highlights_resubmission.tex
Properly edited revised Highlight as per editor's request to keep character length for each bullet below 125
Corrected typo and re-committed

\begin{enumerate}
  \item Coupled linear regression with Principal Component Analysis, PCA, using SVD to obtain a 2D reduced order model
  \item Benchmarked the 2D PCA and linear regression method by comparing with Arithmetric mean, Harmonic mean and PDF models
  \item Demonstrated that the PCA-Linear regression technique can be extended to 3-D models with Higher Order SVD (HOSVD)
  \item Performed a qualitative comparision of the models and simulation results for both the 2D and the 3D cases
  \item The coupled PCA and linear regression model model presented a better representation compared to the other models
\end{enumerate}
\end{document}

>>>>

\begin{enumerate}
  \item Coupled linear regression with Principal Component Analysis (PCA) using SVD, to obtain a 2D reduced order model
  \item Benchmarked the 2D PCA and linear regression method by comparing with Arithmetric mean, Harmonic mean and PDF models
  \item Demonstrated that the PCA-Linear regression technique can be extended to 3D models with Higher Order SVD (HOSVD)
  \item Performed a qualitative comparision of the models and simulation results for both the 2D and the 3D cases
  \item The coupled PCA and linear regression model model presented a better representation compared to the other models
\end{enumerate}
\end{document}
